### 2021-03-12 paper_1.tex
1.4.6

>>>>

\subsubsection{\emph{Robustness to Parameters}}
In order to test the robustness of the model, parameters $ d_r $ and $ \sigma_c $ were used 
in various ranges of $ \{ 1/2, 1/3, 1/4, 1/5, 1/6 \} * min(W,H) $,useful to obtain the 
CBSP. Parameter changes do not cause performance degradation, but show 
that the model is robust across different datasets. Threshold-based selection 
of the object size is a method that still needs to be adapted to the type of 
scene.
